Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-08-17 Manuscript/manuscript.tex
Changed the definition of Relative surf. excess from water-w.r.t.-ions to excess of ions-w.r.t.-water, which is more meaningful for us. Done this both in TeX and script.

The ion binding affinities between different models were compared by calculating
the relative surface excess between water and ions $\Gamma_w^i$ \cite{chattorajBOOK}
\begin{eqnarray}
  \Gamma_w^i   &=& \Gamma_w-\Gamma_i \frac{C_w-C_w'}{C_i-C_i'} \\
  \Gamma_{a} &=& \frac{n_{a} - C_{a} V - C_{a}' V'}{A} \, \, ; \, a=i,w \, ,
\end{eqnarray}
where index $i$ and $w$ denote ions and water respectively,
prime accent denotes the phase inside bilayer, 
whereas non-prime symbols account for bulk water phase,
$n$ is the total amount of water or ions,
$C$ denotes bulk concentrations, 
$V$ is the volume of the respective phase separated by the Gibbs divinding plane, 
$A$ is the area of the interface, 
and $\Gamma_a$ is the surface excess of water or ions. 
As $\Gamma_w^i$ does not depend on the definition of the interfacial region
and the position of the Gibbs dividing plane~\cite{chattorajBOOK},
we consider the whole simulation box as an interface. 
Note that phospholipid membranes are bilayers, 
and hence the interface occurs in the simulation box twice
providing a surface area $2A$.
The concentrations of water and ions inside
the bilayer can be expected to vanish, thus $c_{i,w}'=0$.
This provides us a simplified relation for 
the relative surface excess of lipid bilayers in simulations
\begin{equation}\label{surfexcess}
  \Gamma_w^i=\frac{1}{2A} \left ( n_w - n_i \frac{C_w}{C_i} \right ) ,
\end{equation}
where the bulk concentrations, $C_w$ and $C_i$, can be determined
from the simulation as $C_{bulk}$ in Equation~\ref{eq:conc}.

>>>>

The ion binding affinities between different models were compared by calculating
the relative surface excess of ions with respect to water, $\Gamma_i^w$, as \cite{chattorajBOOK}
\begin{eqnarray}
  \Gamma_i^w   &=& \Gamma_i-\Gamma_w \frac{C_i-C_i'}{C_w-C_w'} \\
  \Gamma_{a} &=& \frac{n_{a} - C_{a} V - C_{a}' V'}{A} \, \, ; \, a=i,w \, ,
\end{eqnarray}
where index $i$ and $w$ denote ions and water respectively,
prime accent denotes the phase inside bilayer, 
whereas non-prime symbols account for bulk water phase,
$n$ is the total amount of water or ions,
$C$ denotes bulk concentrations, 
$V$ is the volume of the respective phase separated by the Gibbs divinding plane, 
$A$ is the area of the interface, 
and $\Gamma_a$ is the surface excess of water or ions. 
As $\Gamma_i^w$ does not depend on the definition of the interfacial region
and the position of the Gibbs dividing plane~\cite{chattorajBOOK},
we consider the whole simulation box as an interface. 
Note that phospholipid membranes are bilayers, 
and hence the interface occurs in the simulation box twice
providing a surface area $2A$.
The concentrations of water and ions inside
the bilayer can be expected to vanish, thus $c_{i,w}'=0$.
This provides us a simplified relation for 
the relative surface excess of lipid bilayers in simulations
\begin{equation}\label{surfexcess}
  \Gamma_i^w=\frac{1}{2A} \left ( n_i - n_w \frac{C_i}{C_w} \right ) ,
\end{equation}
where the bulk concentrations, $C_w$ and $C_i$, can be determined
from the simulation as $C_{bulk}$ in Equation~\ref{eq:conc}.
